---
title: "Weight of Fish"
author: "Bessie Luevano"
date: "Summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
allthat <- read.csv(file = "Fish.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch

```{r}
perch <- filter(allthat,Species=="Perch")
perch <- select(perch,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

I added the model perch and it appears that the best two kind of plots to find the weight would be to use height and width. 

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

Using the summary, it states that the best two variables to use to find the weight are height and width.

# Bream 

```{r}
Bream <- filter(allthat,Species=="Bream")
Bream <- select(Bream,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In this model using Bream it appears the best two variables to use to find the weight would be length 2 and height.

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

Using the summary plot it shows that the best two variable to find the weight are to use length 2 and height. 

# Smelt 

```{r}
Smelt <- filter(allthat,Species=="Smelt")
Smelt <- select(Smelt,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In this model for Smelt, it appears the best variables to use to find the weight are length 2 and height. 

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

Using the summary plot the two best variables to find the weight  will be to use length 2 and width.


# Conclusion

I added three models and summary plots for perch, Bream and smelt in order to find the best two variables to find the weight of each one. The best two variables to use for perch are height and width. The best two variables for Bream to use are length 2 and height and the best two variables to use for smelt are length 2 and width. 

